Mapping Properties of Surface Source Extension

### 2025-03-13 repro/papers/ssefound/paper.tex
interim

\begin{proof}
  For any $alpha \in [0,1)$, $\ldr^{-m}P^*P\ldr^{-m} - \frac{C}{2} \in OPS^0$ is self-adjoint  and its principal symbol $\lxr^{-,m}p_0^Tp_0\lxr^{-m} - \frac{C}{2} \in S^0$ is positive semi-definite. Therefore from Proposition \ref{thm:propa1} there exists $B \in OPS^0$ for which
  \[
    \ldr^{-m}P^*P\ldr^{-1} - \frac{C}{2} = B^*B \mbox{ mod } OPS^{-\infty}
  \]
  or
  \[
    P^*P -\frac{C}{2} \ldr^{2m} = \ldr B^*B \ldr \mbox{ mod } OPS^{-\infty}
  \]
  So for every $N  \in {\bf Z}_+$ there is $C_{K,N} > 0$ so that for $u \in C_0^{\infty}(K)$,  
  \[
    \langle u,P^*P u \rangle \ge \frac{C}{2}\|u\|_m^2 -   C_{K,N}\|u\|^2_{-N}
  \]

@@

\begin{definition} $P \in OPS^m(U,\bR^k)$ is (microlocally) elliptic in the closed conic set $\Gamma \subset T^*(U)$ iff for some $C>0$ its principal symbol $p_0$ satisfies
  \[
    p(x,\xi)^*p(x,\xi) \ge C|\xi|^m
  \]
\end{definition}

\begin{theorem} Suppose that $P \in OPS^m(U,\bR^k)$ is elliptic in the closed conic $\Gamma \subset T^*(U)$. Then for any $Q \in OPS^m(U,\bR)$ with $ES(Q) \subset \Gamma$, $N \in {\bf Z}_+$, and compact $K \subset \subset U$, there exists $C_Q > 0$ and $C_{Q,K,N} \ge 0$ so that for any $u \in C_0^{\infty}(K)$, 
  \[
    \|P(x,D)u\|^2_0  \ge C_Q\|Q(x,D)u\|_0^2 - C_{Q,K,N}\|u\|^2_{-N}.
  \]
\end{theorem}

>>>>

\begin{proof}
$\ldr^{-m}P^*P\ldr^{-m} - \frac{C}{2} \in OPS^0$ is self-adjoint  and its principal symbol $\lxr^{-m}p_0^Tp_0\lxr^{-m} - \frac{C}{2} \in S^0$ is positive semi-definite. Therefore from Proposition \ref{thm:propa1} there exists $B \in OPS^0$ for which
  \[
    \ldr^{-m}P^*P\ldr^{-m} - \frac{C}{2} = B^*B \mbox{ mod } OPS^{-\infty}
  \]
  or
  \[
    P^*P -\frac{C}{2} \ldr^{2m} = \ldr^m B^*B \ldr^m \mbox{ mod } OPS^{-\infty}
  \]
  So for every $N  \in {\bf Z}_+$ there is $C_{K,N} > 0$ so that for $u \in C_0^{\infty}(K)$,  
  \[
    \langle u,P^*P u \rangle \ge \frac{C}{2}\|u\|_m^2 -   C_{K,N}\|u\|^2_{-N}
  \]

@@

\begin{definition} $P \in OPS^m(U,\bR^k)$ is (microlocally) elliptic in the open conic set $\Gamma \subset T^*(U)$ iff for some $C>0$ and conic neighborhood $\Gamma_1 \supset \bar{\Gamma}$, its principal symbol $p_0$ satisfies
  \[
    p(x,\xi)^*p(x,\xi) \ge C|\xi|^m, \, \xi \in \Gamma_1, \, |\xi| \ge 1.
  \]
\end{definition}

Some results from \cite{BaoSy:91b}. Here $0 \le m \le n$, ${\cal N}$ is the normal bundle of the foliation $\bR^n = \bR^{n-m} \times \bR^m$, typically $x \in \bR^{n-m}$ is the parameter, $y \in \bR^m$ is the trace coordinate.

\begin{lemma}
\label{thm:prebao}
Suppose that $k \in {\bf Z}_+$, $n > 0$. Then there exists $C_{k} \ge 0$ so that for $\xi, \eta \in \bR^n$,
\begin{equation}
  \label{eqn:pre}
  (1 + |\xi + \eta|)^{k} \le (1 + |\xi|)^{k} (1 + |\eta|)^{k}
\end{equation}
\end{lemma}
\begin{proof}
  Obvious for $k = 0$. If equation \ref{eqn:pre} holds for $k \in {\bf Z}_+$, then
  \[
    (1 + |\xi + \eta|)^{k+1} \le (1 + |\xi)^{k}(1+ \eta|)^{k}(1+|\xi| + |\eta|)
  \]
  Since $1+|\xi| + |\eta| \le (1+|\xi|)(1 + |\eta|)$, the induction step is done.
\end{proof}

\begin{proposition}
  \label{thm:bao1}
  Suppose that $B \in \Ci(\bR^{n-m},OPS^0(\bR^m)), H \in OPS^0(\bR^n)$, $H$ is a convolution operator, $\phi \in \Ciz(\bR^n)$,
  \[
    ES(H) \cap {\cal N} = \emptyset.
  \]
  Then
  \[
    B\phi H \in OPS^0(\bR^n)
  \]
  and
  \[
    ES(B\phi H) \subset \Pi_2^{-1}(ES(B)) \cap ES(H)
  \]
\end{proposition}

\begin{proof}
  For $u \in \Ciz(\bR^n)$,
  \[
    {\cal F}_x(Hu)(\xi',y) = \int  d\eta H(\xi',\eta')\hat{u}(\xi',\eta)e^{ i y \eta}
  \]
  So
  \[
    (P\phi H)u(x,y) = \int d \xi P(x,y,\xi) {\cal F}_x(\phi Hu)(\xi,y)e^{i x\xi}
  \]
  \[
    =\int d \xi' \int d \xi P(x,y,\xi) {\cal F}_x\phi(\xi-\xi',y) {\cal F}_x(Hu)(\xi',y)e^{i x\xi}
  \]
  \[
   =\int d \xi' \int d \xi \int d\eta P(x,y,\xi) {\cal F}_x\phi(\xi-\xi',y) H(\xi',\eta)\hat{u}(\xi',\eta)e^{i x\xi + i y\eta }
  \]
  \[
    =\int d \xi' \int d \xi \int d\eta P(x,y,\xi) {\cal F}_x\phi(\xi-\xi',y) e^{ix(\xi-\xi')}H(\xi',\eta)\hat{u}(\xi',\eta)e^{i x\xi' + i y\eta }
  \]
  So the symbol of $Q = P \phi H$ is
  \[
    Q(x,y,\xi,\eta) = \int d\xi' P(x,y,\xi') {\cal F}_x\phi(\xi'-\xi,y) e^{i x(\xi'-\xi)}H(\xi,\eta)
  \]
  \[
    = \left(\int d\xi' P(x,y,\xi+\xi') {\cal F}_x\phi(\xi',y) e^{i x\xi'}\right) H(\xi,\eta)
  \]
  From the definition of $S^0_{1,0}$, for $(x,y)$ ranging over a compact $K \subset \bR^n$ , and any $\alpha \in {\bf Z}_+^m$, there is $C_{K,|\alpha|} > 0$ so that
  \[
    |\partial^{\alpha}_{\xi} P(x,y,\xi)| \le C_{K,|\alpha|}(1 + |\xi|)^{-|\alpha|}
  \]
  so for $(x,y) \in K, \alpha=(\alpha_1,\alpha_2) \in {\bf Z}_+^m \times {\bf Z}_+^{n-m}$,
  \[
    |\partial_{\xi,\eta}^{\alpha} Q(x,y,\xi,\eta)|
  \]
  \[
    \le \sum_{\alpha_1' \le \alpha_1} \left|\left(\partial_{\xi}^{\alpha_1'}  \int d\xi' P(x,y,\xi+\xi') {\cal F}_x\phi(\xi',y) e^{i x\xi'}\right)\partial_{\xi}^{\alpha_1-\alpha_1'} \partial_{\eta}^{\alpha_2}H(\xi,\eta)       \right|
  \]
  \[
    \le C \sum_{\alpha_1' \le \alpha_1} \left|\left(  \int d\xi' (1 + |\xi+\xi'|)^{-|\alpha_1'|} {\cal F}_x\phi(\xi',y) e^{i x\xi'}\right)\partial_{\xi}^{\alpha_1-\alpha_1'} \partial_{\eta}^{\alpha_2}H(\xi,\eta)       \right|
  \]
  Rearranging the conclusion of Lemma \ref{thm:prebao},
  \[
    (1 + |\xi + \xi'|)^{-k} \le (1+|\xi|)^k(1+|\xi'|)^{-k},
  \]
  so
  \[
    |\partial_{\xi,\eta}^{\alpha} Q(x,y,\xi,\eta)| \le C \sum_{\alpha_1' \le \alpha_1} (1 + |\xi|)^{-|\alpha_1'|}|\partial_{\xi}^{\alpha_1-\alpha_1'}\partial_{\eta}^{\alpha_2}H(\xi,\eta) |
  \]
  \[
    \le C \sum_{\alpha_1' \le \alpha_1} (1 + |\xi|)^{-|\alpha_1'|}(1 + |(\xi,\eta)|)^{-|\alpha_1|+|\alpha_1'|-\alpha_2}
  \]
  since $H \in S^0_{1,0}(\bR^n)$. From norm equivalence, can replace $|(\xi,\eta)|$ with $|\xi| + |\eta|$   for the price of changing $C$.  So the above is
  \[
    \le C \sum_{\alpha_1' \le \alpha_1} (1 + |\xi|)^{-|\alpha_1'|}(1 + |\xi| + |\eta|)^{-|\alpha_1|+|\alpha_1'|-|\alpha_2|}
  \]
  \[
    \le C \sum_{\alpha_1' \le \alpha_1} (1 + |\xi|+ |\eta|)^{-|\alpha_1'|}(1 + |\xi| + |\eta|)^{-|\alpha_1|+|\alpha_1'|-|\alpha_2|}
  \]
  \[
    \le C (1 + |\xi| + |\eta|)^{-|\alpha_1|-|\alpha_2|} \le C(1 + |(\xi,\eta)|)^{-|\alpha|}
  \]
  whence $Q \in S^{0}_{1,0}(\bR^n)$.
